Solar jet observed at the limb in SDO/SST

### 2016-04-21 paper/ms_temp_paper.tex

% DOCUMENT PREAMBLE
\documentclass{emulateapj}
% \documentclass[referee]{apj}

\usepackage{graphicx}
\usepackage{float}

@@

\begin{document}

@@

\begin{figure}[]
	\includegraphics[width=\columnwidth]{../figures/STEREO-A.png} 
	\caption{HI $30.4$ nm images at $07:26:15$, $07:36:15$, $07:46:15$ and $07:56:15$ going from left to right.}
\end{figure}

>>>>

% DOCUMENT PREAMBLE
\documentclass{emulateapj}
% \documentclass[referee]{apj}
\usepackage{pythontex}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% PythonTeX Bug Fix % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% pytexbug fix for context in customcode.
\makeatletter
\renewenvironment{pythontexcustomcode}[2][begin]{%
    \VerbatimEnvironment
    \Depythontex{env:pythontexcustomcode:om:n}%
    \ifstrequal{#1}{begin}{}{%
        \ifstrequal{#1}{end}{}{\PackageError{\pytx@packagename}%
            {Invalid optional argument for pythontexcustomcode}{}
        }%
    }%
    \xdef\pytx@type{CC:#2:#1}%
    \edef\pytx@cmd{code}%
    % PATCH \def\pytx@context{}%
    \pytx@SetContext
    % END PATCH
    \def\pytx@group{none}%
    \pytx@BeginCodeEnv[none]}%
{\end{VerbatimOut}%
\setcounter{FancyVerbLine}{\value{pytx@FancyVerbLineTemp}}%
\stepcounter{\pytx@counter}%
}%
\makeatother
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\setpythontexcontext{figurewidth=\the\columnwidth}
\newcommand{\includepgf}[1]{\IfFileExists{#1}{\input{#1}}{}}

\usepackage{graphicx}
\usepackage{pgf}
\usepackage{float}
\usepackage{import}
\usepackage{cleveref}
\crefname{equation}{Equation}{Equations}
\crefname{figure}{Figure}{Figures}
\crefname{section}{Section}{Sections}
\crefname{table}{Table}{Tables}

@@

\begin{document}
\begin{pythontexcustomcode}{py}
import texfigure
texfigure.configure_latex_plots(pytex, font_size=8)

pytex.formatter = texfigure.repr_latex_formatter

import matplotlib.pyplot as plt

manager = texfigure.Manager(pytex, '../')
\end{pythontexcustomcode}

@@

\begin{pycode}
from sunpy.data.sample import AIA_171_IMAGE
import sunpy.map

aiamap = sunpy.map.Map(AIA_171_IMAGE)

fig = plt.figure()
im = aiamap.plot()

lfig = manager.save_figure('sunpy1', fig)
lfig.caption = r"EUV image of the million degree solar corona, taken with the Atmospheric Imaging Assembly on the NASA Solar Dynamics Observatory."
\end{pycode}

\py|lfig|

Look the sun is in \cref{fig:sunpy1}.
